---
title: "Modernization of Title X Family Planning Analysis: Data Cleaning"
author: "Roa'a Hamed"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

This document turns the original replication data into the analysis dataset
`data/modernization_data.rds`. It is an R translation of the earlier Stata
do-file (`modernization_datacleaning.do`), so Stata is not needed.

**Inputs** (from Bailey's replication package; see `README.md`), placed in `data/`:

- `vs_fo_final.dta`: county-year panel.
- `table1data.dta`: county covariates. It has **no FIPS identifier**.

**What it does**

1. Recovers the unrounded 1960 baseline covariates. The panel only stores them as
   detrended terms (`D_*_t` = baseline level x year), so dividing by `year` recovers them.
2. Attaches FIPS codes to `table1data.dta` by matching its seven demographic
   variables to the recovered 1960 values.
3. Merges the extra covariates (1960 population, education, region) onto the full panel by FIPS.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Packages and file paths

```{r config}
required_pkgs <- c("haven", "dplyr", "purrr", "tibble")
missing_pkgs <- setdiff(required_pkgs, rownames(installed.packages()))
if (length(missing_pkgs) > 0) {
  stop("Please install: ", paste(missing_pkgs, collapse = ", "), call. = FALSE)
}

library(haven)
library(dplyr)
library(purrr)
library(tibble)

data_dir        <- "data"
raw_panel_file  <- file.path(data_dir, "vs_fo_final.dta")
raw_table1_file <- file.path(data_dir, "table1data.dta")
out_file        <- file.path(data_dir, "modernization_data.rds")

input_files <- c(raw_panel_file, raw_table1_file)
absent <- input_files[!file.exists(input_files)]
if (length(absent) > 0) {
  stop("Missing input file(s): ", paste(absent, collapse = ", "),
       "\nDownload them from the replication package (see README.md) into ", data_dir, "/",
       call. = FALSE)
}

# Detrended variables in the panel, and the baseline names they map to
# e.g. D_60pcturban_t  ->  _60pcturban
detrended_vars <- c(
  "D_pct59incge10k_t", "D_pct59inclt3k_t", "D_60pctnonwhit_t", "D_60pctrurf_t",
  "D_60pcturban_t", "D_60pctmt64years_t", "D_60pctlt5years_t"
)
baseline_vars <- sub("_t$", "", sub("^D_", "_", detrended_vars))

# Covariates that exist only in table1data.dta
extra_vars <- c("_60totpop", "_60pcteducge12yr", "_60pcteduclt4yr", "NE", "MW", "S", "W")

# Stata's `gen` stores single-precision floats. Emulate that so results match the
# original Stata output exactly.
as_float32 <- function(x) {
  x <- as.numeric(x)
  out <- readBin(writeBin(x, raw(), size = 4), what = "numeric", n = length(x), size = 4)
  out[is.na(x)] <- NA_real_
  out
}
```

## Step 1: Recover the unrounded baseline covariates

```{r detrend}
panel <- read_dta(raw_panel_file)
stopifnot(all(detrended_vars %in% names(panel)))

for (i in seq_along(detrended_vars)) {
  panel[[baseline_vars[i]]] <- as_float32(
    as.numeric(panel[[detrended_vars[i]]]) / as.numeric(panel[["year"]])
  )
}

# The 1960 snapshot (one row per county) is the bridge that carries FIPS codes
bridge <- panel %>%
  filter(as.numeric(year) == 60) %>%
  select(fips, all_of(baseline_vars))

stopifnot(!anyNA(bridge[baseline_vars]), !anyDuplicated(bridge$fips))
cat("Counties in 1960 bridge:", nrow(bridge), "\n")
```

## Step 2: Attach FIPS codes to `table1data.dta`

Each `table1data` row is matched to the 1960 county whose seven baseline values are
closest. The Stata version matched on these values rounded to three decimals; the
tolerance below (0.0005) gives the same pairing without depending on how rounding
behaves at exact boundaries. The code stops if any row lacks a match or if two rows
match the same county, so a bad match cannot pass silently.

```{r match-fips}
table1 <- read_dta(raw_table1_file)
stopifnot(all(c(baseline_vars, extra_vars) %in% names(table1)))

B  <- sapply(bridge[baseline_vars], as.numeric)   # counties x 7 (from the panel)
T1 <- sapply(table1[baseline_vars], as.numeric)   # counties x 7 (from table1data)
stopifnot(!anyNA(T1))

tol <- 5e-4

# For each table1data row: index of the closest bridge row and the worst-case gap
best <- vapply(seq_len(nrow(T1)), function(i) {
  gap <- apply(abs(sweep(B, 2, T1[i, ], "-")), 1, max)
  j <- which.min(gap)
  c(j = as.numeric(j), dist = gap[j])
}, FUN.VALUE = c(j = 0, dist = 0))

match_tbl <- tibble(b_row = best["j", ], dist = best["dist", ])

n_matched   <- sum(match_tbl$dist < tol)
n_duplicate <- sum(duplicated(match_tbl$b_row))
cat("table1data rows:", nrow(T1), "\n")
cat("Matched within tolerance:", n_matched, "\n")
cat("Rows matched to a county already used:", n_duplicate, "\n")

if (n_matched != nrow(T1) || n_duplicate > 0 || nrow(T1) != nrow(bridge)) {
  stop("FIPS matching failed: expected a one-to-one match of every county.", call. = FALSE)
}

covariates_to_add <- tibble(fips = bridge$fips[match_tbl$b_row]) %>%
  bind_cols(table1[extra_vars])
```

## Step 3: Merge onto the full panel

```{r merge}
panel <- panel %>%
  left_join(covariates_to_add, by = "fips", relationship = "many-to-one")

stopifnot(all(panel$fips %in% covariates_to_add$fips))

cat("Rows:", nrow(panel), "| Counties:", n_distinct(panel$fips), "\n")
saveRDS(panel, out_file)
cat("Saved", out_file, "\n")
```

## Optional check against the old Stata output

If you also have the dataset made by the original Stata do-file, save it as
`data/modernization_data.dta` and this chunk compares every added column. Otherwise
it is skipped. Differences should be zero or on the order of floating-point error.

```{r compare-stata, eval = file.exists(file.path("data", "modernization_data.dta"))}
stata_version <- read_dta(file.path("data", "modernization_data.dta"))
stopifnot(identical(as.numeric(stata_version$fips), as.numeric(panel$fips)),
          identical(as.numeric(stata_version$year), as.numeric(panel$year)))

map_dfr(c(baseline_vars, extra_vars), function(v) {
  tibble(variable = v,
         max_abs_diff = max(abs(as.numeric(panel[[v]]) - as.numeric(stata_version[[v]])),
                            na.rm = TRUE))
})
```

## Notes on the data

- `NE`, `MW`, `S` and `W` are coded 0/100 rather than 0/1. The analysis treats any value above 0 as membership.
- `_60pcteducge12yr` has a maximum above 100, which cannot be a percentage. It is carried through unchanged from the source data; check it before relying on that covariate.
